Testing for measurement invariance with respect to an ordinal variable

### 2013-03-21 ordinal/ordinal.Rnw
Simulation & Results: o Modified code to deal with small bug in lavaan which involves   the Satorra-Bentler test stat. o Obtained new results for both Simulation 1 and Simulation 2.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/semtools@193 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

## auxiliary code
source("../www/mz-ordinal.R")
## TODO Change this:
source("../www/estfun-lavaan.R")
source("../www/efpFunctional-cat.R")
source("../www/sim-ordinal.R")

@@

<<sim2>>=
if(file.exists("sim2.rda")) {
  load("sim2.rda")
} else {
  sim2 <- simulation(diff = seq(0, 3, by = 0.5), nobs = c(1200, 4800, 9600), anomaly = TRUE)
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=",levels(sim2$nlevels),sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=",levels(sim2$nobs),sep="")
  levels(sim2$test) <- c("LM_uo", "LRT", "LM_o", "WDM_o")
  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("LM_o", "WDM_o", "LRT", "LM_uo"),
  labels = c("maxLM_o", "WDM_o", "LRT", "LM_uo"))
@

>>>>

## auxiliary code
source("../www/mz-ordinal.R")
source("../www/estfun-lavaan.R")
source("../www/efpFunctional-cat.R")
source("../www/sim-ordinal.R")

@@

<<sim2>>=
if(file.exists("sim2.rda")) {
  load("sim2.rda")
} else {
  sim2 <- simulation(diff = seq(0, 3, by = 0.5), nobs = c(1200, 4800, 9600), anomaly = TRUE)
  sim2$nlevels <- factor(sim2$nlevels)
  levels(sim2$nlevels) <- paste("m=",levels(sim2$nlevels),sep="")
  sim2$nobs <- factor(sim2$nobs)
  levels(sim2$nobs) <- paste("n=",levels(sim2$nobs),sep="")
  levels(sim2$test) <- c("AIC","LM_uo", "LRT", "LRT_sb","LM_o", "WDM_o",
                         "YB97")
  save(sim2, file="sim2.rda")
}
sim2$test <- factor(as.character(sim2$test),
  levels = c("LM_o", "WDM_o", "LRT", "LM_uo", "LRT_sb",
             "YB97", "AIC"),
  labels = c("maxLM_o", "WDM_o", "LRT", "LM_uo", "LRT_sb", "YB97", "AIC"))
@
